Title

### 2018-07-28 thesis/paper/paper.tex
Added table and description

\usepackage{rotating}
\usepackage{float}
\restylefloat{table}
\usepackage{makecell}
\renewcommand{\cellalign}{tl}
\usepackage{tabularx}
\usepackage{todonotes}

@@

%\begin{table}[t]
%\caption{property constraints and basic information}\label{tab_basestats}
%\begin{tabular}{rcl}

%\# of properties & constraint id & constraint name \\
%\hline
%4265 & Q21503247 & Item requires statement \\
%3021 & Q21502404 & Format \\
%2909 & Q19474404 & Single value \\
%2843 & Q21502410 & Unique value \\
%2613 & Q21503250 & Type \\
%1410 & Q53869507 & Scope \\
%781 & Q21502838 & Conflicts with \\
%707 & Q21510865 & Value type \\
%343 & Q21514353 & Allowed units \\
%303 & Q21510851 & Allowed qualifiers \\
%244 & Q21510864 & Value requires statement \\
%203 & Q21510856 & Mandatory qualifier \\
%188 & Q21510860 & Range \\
%119 & Q21510855 & Inverse \\
%116 & Q21510859 & One of \\
%106 & Q52848401 & Integer \\
%65 & Q51723761 & No bounds \\
%53 & Q21510852 & Commons link \\
%33 & Q21510862 & Symmetric \\
%27 & Q52004125 & Allowed entity types \\
%17 & Q52558054 & None of \\
%13 & Q21510857 & Multi-value \\
%10 & Q54554025 & Link \\
%6 & Q21510854 & Difference within range \\
%3 & Q52060874 & Single best value \\
%1 & Q25796498 &  \\
%1 & Q52712340 &  \\
%
%\end{tabular}
%\end{table}
To improve the data quality, help editors avoid common mistakes and clarify the usage of properties, Wikidata allows constraints to be defined on properties. They are however not firm rules and exceptions can and should be made if necessary. A property constraint says something about the way a property may or may not be used. This can mean simple restrictions on the statement a property is part of, e.g. only certain values are allowed or more complex requirements on connected parts of the data graph, e.g. the value of a statement with this property should have certain statements. On the following page you can find table \ref{tab_basestats} which list the existing property constraints and a short description as well as classifying information which will be explained shortly. Afterwards the constraints will be explained in detail and either a basic approach for their modelling or reasoning why it is not possible or sensible to model it given.\\

@@

>>>>

\usepackage{rotating}
\usepackage{float}
\restylefloat{table}
\usepackage{makecell}
\renewcommand{\cellalign}{tl}
\usepackage{tabularx}
\usepackage{todonotes}
\usepackage{adjustbox}

@@

To improve the data quality, help editors avoid common mistakes and clarify the usage of properties, Wikidata allows constraints to be defined on properties. They are however not firm rules and exceptions can and should be made if necessary. A property constraint says something about the way a property may or may not be used. This can mean simple restrictions on the statement a property is part of, e.g. only certain values are allowed or more complex requirements on connected parts of the data graph, e.g. the value of a statement with this property should have certain statements. Further down you can find table \ref{tab_property_constraints}, which list the existing property constraints. Afterwards the constraints will be explained in detail and either a basic approach for their modelling or reasoning why it is not possible or sensible to model it given.\\

@@

Table \ref{tab_property_constraints} shows all currently used property constrains in Wikidata. It is sorted by difficulty, which is an estimate of the necessary pre-processing and rule complexity based on required features. These required features are conditions that cannot natively be expressed in datalog and would require some kind of pre-processing to be made available. Difficulty 0 does not need any pre-processing except for loading the data into datalog as ground rules. 1 requires inequality, which can be easily solved with brute force but will be improved in chapter \ref{cha_rules}. 2 needs negation in a form that can be solved without pre-processing everything and 3 in a form that would require all logic as part of pre-processing. Other features needed for category three are regular expressions, which could theoretically be translated but would require large amounts of pre-processing, value comparison, general negation and finally web requests to test if a link is valid.

\begin{table}[H]
\caption{property constraints}\label{tab_property_constraints}
\begin{tabularx}{\textheight}{rrllllX}
Difficulty & \makecell{\# constrained\\ properties} & Identifier & Name & Required Features \\
\hline
0 & 1410 & Q53869507 & Scope &  \\
0 & 781 & Q21502838 & Conflicts with &  \\
0 & 27 & Q52004125 & Allowed entity types &  \\
0 & 17 & Q52558054 & None of &  \\
1 & 2843 & Q21502410 & Distinct value & Inequality \\
1 & 343 & Q21514353 & Allowed units & Inequality \\
1 & 303 & Q21510851 & Allowed qualifiers & Inequality \\
1 & 116 & Q21510859 & One of & Inequality \\
1 & 3 & Q52060874 & Single best value & Inequality \\
1 & 1 & Q52712340 & One-of qualifier value & Inequality \\
2 & 4265 & Q21503247 & Item requires statement & Negation (statement non-existence) \\
2 & 244 & Q21510864 & Value requires statement & Negation (statement non-existence) \\
2 & 119 & Q21510855 & Inverse & Negation (statement non-existence) \\
2 & 33 & Q21510862 & Symmetric & Negation (statement non-existence) \\
2 & 13 & Q21510857 & Multi-value & Negation, Count (up to two) \\
2 & 2909 & Q19474404 & Single value & Inequality, partially negation (qualifier non-existence) \\
2 & 203 & Q21510856 & Mandatory qualifier & Negation (qualifier non-existence) \\
3 & 2613 & Q21503250 & Type & Negation (derived fact negation) \\
3 & 707 & Q21510865 & Value type & Negation (derived fact negation) \\
3 & 3021 & Q21502404 & Format & Regular expressions \\
3 & 188 & Q21510860 & Range & Value comparison \\
3 & 106 & Q52848401 & Integer & Regular expressions \\
3 & 65 & Q51723761 & No bounds & Negation \\
3 & 53 & Q21510852 & Commons link & Web request \\
3 & 10 & Q54554025 & Link & Negation \\
3 & 6 & Q21510854 & Difference within range & Value comparison \\
3 & 1 & Q25796498 & Contemporary constraint & Negation \\
\end{tabularx}
\end{table}
